\bf Mayo Pharmacy Optimization Case Study\\ \large Using Discrete Event Simulation

### 2019-12-08 Mayo/Final Draft/Draft.tex
PNG, axes fixed
Worked a little at work lol

\title{\bf Mayo Case Study Rough Draft\\

@@

\tableofcontents                        % Print table of contents

@@

In this case study, we are tasked with both modeling and optimizing the workflow for a pharmacy based on samples of data regarding task duration and incoming order frequency. In addition to the sample data for the pharmacy, we are also given a brief overview of the basic workflow for the pharmacy. Using this information, we shall begin by constructing a discrete event simulation in C++ to test our so called ``control" case, i.e. the pharmacy described by the basic information. Once this simulation is running and tested, we shall attack the optimization on two fronts.

@@

In order to construct our discrete event simulation in C++, we must first identify the basic workflow in the pharmacy. This workflow is tied to both legal regulations as well as potentially company specific guidelines. This workflow will form the backbone for our simulations main loop. The second stage of development is centered around identifying the distributions from the time sample data provided. In order to run the simulation, we need to know the distributions that each time variable comes from. Finally, we run the simulation and report statistical analysis on the results.

@@

>>>>

\title{\bf Mayo Pharmacy Optimization Case Study\\

@@

%\tableofcontents                        % Print table of contents

@@

Prescription medication is becoming increasingly commonplace in the United States. In 2013, the average number of prescriptions per capita was $12.2$, up from $9$ in 1998 [CITE BOTH]. With this trend in preccription usage on the rise still, pharmacies are becoming an ever greater presence in the lives of americans. As such, pharmacies need to adapt to deal with increasing numbers of orders, as well as increasing the speed and accuracy at which they fill orders, in order to remain competitive in an increasingly saturated landscape of pharmacies.  Consequently, pharmacies must adapt their methodologies and staffing reqirements in order to maximimize the numebr of orders filled and minimize the wait time and employee idle times. Obviously, testing multiple different prioritizations and staffing numbers is both expensive and time consuming, so we shall consider a discrete event simulation approach. In this case study, we are tasked with both modeling and optimizing the workflow for a pharmacy based on samples of data regarding task duration and incoming order frequency. In addition to the sample data for the pharmacy, we are also given a brief overview of the basic workflow for the pharmacy. Using this information, we shall begin by constructing a discrete event simulation in C++ to test our so called ``control" case, i.e. the pharmacy described by the basic information. Once this simulation is running and tested, we shall attack the optimization on two fronts.

@@

\section*{Background}
\addcontentsline{toc}{section}{Background}
In our prototypical example, there are six basic tasks in the workflow tied to the two different types of orders, oral and IV: order entry, entry verification, oral fill, iv fill, fill verification, and dispensing through the window. In addition to these tasks, there are two different classes of employee [Pharmacist and Technician], who are constrained as to which task they may perform due to both legal regulations as well as potentially company specific guidelines. These regulations dictate that of the tasks, the verification tasks can only be performed by the pharmacists, while the remaining 3 tasks can be performed by both pharmacists and technicians. A breakdown of this hienarchy follows in Table \ref{table:tasks}, with pharmacist specific tasks highlighted in red.
\begin{table}[h]

@@

The workflow of this pharmacy follows a fairly linear task order as one might expect from the tasks named above, and is illustrated graphically in Figure \ref{fig:flowchart}.
We see that the workflow only diverges from being liear at the fill stage of the process, and this is due to the fact that one employee is solely tasked with filling IV orders in isolation.
In order to construct our discrete event simulation in C++, we must first identify the basic workflow in the pharmacy. This  This workflow will form the backbone for our simulations main loop. The second stage of development is centered around identifying the distributions from the time sample data provided. In order to run the simulation, we need to know the distributions that each time variable comes from. Finally, we run the simulation and report statistical analysis on the results.
